---
title: "HMRFEM Model"
author: "Yuan Mei"
date: "4/07/2017"
output: pdf_document
---

## Step 0: Load the packages, specify directories

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(text2vec, dplyr, qlcMatrix, kernlab, knitr)
library("stringr")

setwd("~/GitHub/Spr2017-proj4-team1/data")
# here replace it with your own path or manually set it in RStudio
# to where this rmd file is located
```

## Step 1: Load and process the data
```{r}
#get author_id, paper_id, coauthor_list, paper_title, journal name
data.lib="~//GitHub/Spr2017-proj4-team1/data/nameset"
data.files=list.files(path=data.lib, "*.txt")
data.files
### remove "*.txt"
query.list=substring(data.files, 
                     1, nchar(data.files)-4)

query.list
## add a space
query.list=paste(substring(query.list, 1, 1), 
                 " ", 
                 substring(query.list, 
                           2, nchar(query.list)),
                 sep=""
)

query.list

# Write a function to get the list of author_id, paper_id, coauthor_list, paper_title, journal name

f.line.proc=function(lin, nam.query="."){
  
  # remove unwanted characters
  char_notallowed <- "\\@#$%^&?" 
  lin.str=str_replace(lin, char_notallowed, "")
  
  # get author id
  lin.str=strsplit(lin.str, "_")[[1]]
  author_id=as.numeric(lin.str[1])
  
  # get paper id
  lin.str=lin.str[2]
  paper_id=strsplit(lin.str, " ")[[1]][1]
  lin.str=substring(lin.str, nchar(paper_id)+1, nchar(lin.str))
  paper_id=as.numeric(paper_id)
  
  # get coauthor list
  lin.str=strsplit(lin.str, "<>")[[1]]
  coauthor_list=strsplit(lin.str[1], ";")[[1]]
  
  #print(lin.str)
  for(j in 1:length(coauthor_list)){
    if(nchar(coauthor_list[j])>0){
      nam = strsplit(coauthor_list[j], " ")[[1]]
      if(nchar(nam[1])>0){
        first.ini=substring(nam[1], 1, 1)
      }else{
        first.ini=substring(nam[2], 1, 1)
      }
    }
    last.name=nam[length(nam)]
    nam.str = paste(first.ini, last.name)
    coauthor_list[j]=nam.str
  }
  
  match_ind = charmatch(nam.query, coauthor_list, nomatch=-1)
  
  #print(nam.query)
  #print(coauthor_list)
  #print(match_ind)
  
  if(match_ind>0){
    
    coauthor_list=coauthor_list[-match_ind]
  }
  
  paper_title=lin.str[2]
  journal_name=lin.str[3]
  
  list(author_id=author_id, 
       paper_id=paper_id, 
       coauthor_list=coauthor_list, 
       paper_title=paper_title, 
       journal_name=journal_name)
}

#read data
data_list=list(1:length(data.files))

for(i in 1:length(data.files)){
  
  dat=as.list(readLines(paste(data.lib, data.files[i], sep="/")))
  data_list[[i]]=lapply(dat, f.line.proc, nam.query=query.list[i])
  
  
}
names(data_list)=query.list
```

## Step 2: Feature design
Let's first create a vocabulary-based DTM. Here we collect unique terms from all documents and mark each of them with a unique ID using the  `create_vocabulary()` function. We use an iterator to create the vocabulary.
```{r}
it_train_list <- list(1:length(data.files))
vocab <- list(1:length(data.files))
author_id<-list(1:length(data.files))
for (j in 1:length(data.files)) {
  data_unlist <- unlist(data_list[[j]])
  paper_title<- as.vector(data_unlist[which(names(data_unlist)=="paper_title")])
  paper_id<- as.vector(data_unlist[which(names(data_unlist)=="paper_id")])
  author_id[[j]]<- as.vector(data_unlist[which(names(data_unlist)=="author_id")])
  it_train_list[[j]] <- itoken(paper_title, 
             preprocessor = tolower, 
             tokenizer = word_tokenizer,
             ids =paper_id,
             progressbar = FALSE)
vocab[[j]] <- create_vocabulary(it_train_list[[j]], stopwords = c("a", "an", "the", "in", "on",
                                                   "at", "of", "above", "under"))

vocab[[j]]
  
  
}
```

Here, we remove pre-defined stopwords, the words like ??a??, ??the??, ??in??, ??I??, ??you??, ??on??, etc, which do not provide much useful information. 

Now that we have a vocabulary list, we can construct a document-term matrix.
```{r}
#construct DTM
vectorizer <- list(1:length(data.files))
dtm_train <- list(1:length(data.files))
for(i in 1:length(data.files)){
  vectorizer[[i]] <- vocab_vectorizer(vocab[[i]])
  dtm_train[[i]] <- create_dtm(it_train_list[[i]], vectorizer[[i]])
}

```

Now we have DTM and can check its dimensions.
```{r}
for (i in 1:length(data.files)){
print(dim(dtm_train[[i]]))
}
```


Then, we want to use DTM to compute TF-IDF transformation on DTM.
```{r}
dtm_train_tfidf  <- list(1:length(data.files))

for(i in 1:length(data.files)){
tfidf <- TfIdf$new()
dtm_train_tfidf[[i]] <- fit_transform(dtm_train[[i]], tfidf)
}

```

## Step 3: Write HMRF EM Algorithm

Define distance function D(xi,xj)
```{r}
# This function compute the distance as described in the paper using a (squared) matrix A and two vectors of the same length. Vectors must have the same lenght of the dimention of the matrix. 
distance = function(A,xi,xj){
  A = as.matrix(A)
  xi = as.matrix(xi)
  xj = as.matrix(xj)
  normxi = sqrt(crossprod(xi,A)%*% xi)[1]
  normxj = sqrt(crossprod(xj,A)%*% xj)[1]
  return(1 - (crossprod(xi,A) %*% xj)[1]/(normxi*normxj))
}
```



Define contraints 2& 6
```{r}
M <- list(1:length(data.files))
for (d in 1:length(data.files)){
  #calculate n and p
  n <- length(data_list[[d]])
  group <- data_list[[d]]
  coauthor_list <- vector(length=0)
  for(j in 1:n){
    coauthor_list_add <- group[[j]]$coauthor_list
    coauthor_list <-c(coauthor_list,coauthor_list_add)
  }
  coauthor_list <- unique(coauthor_list)
  p <- length(coauthor_list)
  
  #construct submatrix
  #construct Mp
  Mp <- diag(n)
  #construct Map
  Map <- Matrix(rep(0,n*p),p,n)
  for(j in 1:p){
    for(i in 1:n){
       Map[j,i] =ifelse(coauthor_list[j] %in% group[[i]]$coauthor_list,1,0)
       #whether aj is the co-author in pi
    }
        }
  #transform the Matrix
  #construct Mpa
  Mpa <- t(Map)
  
  #construct Ma(let's limit our database in the data_list)
  Ma <- Matrix(rep(0,p^2),p,p)
  for (i in 1:p){
    for(j in 1:p){
      #Ma[i,j]=1 indicates coauthor_i and coauthor_j in the same publication
      #if both Map[i,m]=1 & Mpa[m,j]=1, Ma[i,j]=1
         Ma[i,j]=ifelse(Map[i,]%*%Mpa[,j]>0,1,0)
    }
  }

    
  M[[d]] <- cbind(rbind(Mp,Map),rbind(Mpa,Ma))
}

M1 <- list(1:length(data.files))
for (d in 1:length(data.files)){
  M1[[d]] <- M[[d]]%*%M[[d]]
}

##Assume t=2, then we get 2-coauthor constraint
M2 <- list(1:length(data.files))
for (d in 1:length(data.files)){
  M2[[d]] <- M[[d]]%*%M[[d]]%*%M[[d]]
}

constraint2 <-function(i,j,d){
  c6<-ifelse(M1[[d]][i,j]>=1,1,0)
  return(c6)
}

constraint6 <-function(i,j,d){
  c6<-ifelse(M2[[d]][i,j]>=1,1,0)
  return(c6)
}

#We only tried until 3, which is enough. We get a tao, which is a matrix between papers
```


Objective Function 
```{r}
# This function compute the objective function at the point defined by the distance matrix D , the vector of labels l and the Matrix Y of centroids. The name and the number of document is also required. w2 and w6 and t are three hyperparameters fixed at w2 = 0.7 and w6 = w2**t with t = ?. d is the author name number (Gupta is number 1), k the number of cluster. 

#number of clusters:
#k=length(unique(author_id))

objective = function(A, l, Y, d, w2 = 0.7, w6 = 0.7^2){
  obj = 0
  for(i in dim(dtm_train_tfidf[[d]])[1]){
    for(j in dim(dtm_train_tfidf[[d]])[1]){
      obj = obj + (l[i]==l[j]) * distance(A,as.matrix(dtm_train_tfidf[[d]])[i,],as.matrix(dtm_train_tfidf[[d]])[j,]) * (w2 * constraint2(i,j,d) + w6 * constraint6(i,j,d))
    }  
  }
  for(i in dim(dtm_train_tfidf[[d]])[1]){
    obj = obj + distance(A,as.matrix(dtm_train_tfidf[[d]])[i,],Y[l[i],])
  }
  return(obj)
}
 
```


Hmrf-em algorithm
#initiialization
```{r}
#Initialization
Initialization <-function(A,d){
  #create index set
  index=1:dim(dtm_train_tfidf[[d]])[1]
  #define label
  l=vector()
  #initial label
  lambda=0
  index_new=index
  
  while(length(index)>0){
     lambda=lambda+1
     #print(paste("lambda=",lambda))
     
    for (j in index){
    i=index[1]
    if(constraint2(i,j,1)>0|constraint6(i,j,1)>0)
      {
    dele = which(index_new==j)
    index_new <- index_new[-dele]#remove index already belong to a cluster
    l[j]=lambda
     }
    }
    index=index_new
    #print(paste("index=",index[1],"length=",length(index)))
  }
  
  if(lambda<k){
    
      for(i in 1:lambda){
        #calculate centroids
    X = as.matrix(dtm_train_tfidf[[d]])[l==i,] #subset the Xi to the one with the label
    Y=matrix(NA,lambda,dim(dtm_train_tfidf[[d]])[2])
    Y[i,] = Y[i,]/(sqrt((t(Y[i,]) %*% A %*% Y[i,])[1]))
      }
    glo_Y = rowSums(Y)
    glo_Y =glo_Y/(sqrt((t(glo_Y) %*% A %*% glo_Y)[1]))
    while(k-lambda>0){
      lambda=lambda+1
      Y[lambda,]=glo_Y+rnorm(n=dim(dtm_train_tfidf[[d]])[2],mean=0,sd=(3)^(1/3))
    }
    l=Estep(A, l, Y, d, k , w2 = 0.7, w6 = 0.7^2)
    }
  
  
  else if(lambda>k){

    X = as.matrix(dtm_train_tfidf[[d]])
    #calculate the distances between clusters and combine the closest together
   #too slow so deciede to use kmeans
    #while(lambda-k>0){
       Y=matrix(NA,lambda,dim(dtm_train_tfidf[[d]])[2])
      for(i in 1:lambda){
        #calculate centroids
    Z=as.matrix(X[l==i,],ncol=dim(dtm_train_tfidf[[d]])[2])#subset the Xi to the one with the label
    Y[i,] = colSums(Z)
    Y[i,] = Y[i,]/(sqrt((t(Y[i,]) %*% A %*% Y[i,])[1]))
      }
      cluster_label=kmeans(Y,centers=k)$cluster
      #re-order the cluster number
      

      uni=unique(cluster_label)
      for(j in 1:k){
        loc=which(cluster_label==uni[j])
        
        for(i in loc){
        l[l==i]=j
        }
      }
      
      
     
      #calculate distances between cluster j and cluster h
       #we create an upper matrix. we assign half of the values as a very large number.
     # dis=matrix(100,lambda,lambda)
      #for(j in 1:lambda){
      #  for(h in (j+1):lambda){
      #    dis[j,h]=distance(A,Y[j,],Y[h,])
      #    print(dis[j,h])
      #  }
    #  }
      #find the closest two clusters and assign the larger index cluster to the lower index              cluster
    #k1=which(dis==min(dis),arr.ind=TRUE)[1]
    #k2=which(dis==min(dis),arr.ind=TRUE)[2]
    #l[l==max(k1,k2)]=min(k1,k2)
    #lambda=lambda-1
   # }
  }
  return(l)
}
```

```{r}
# - first clustering respecting the constraints c2 and c6 in k groups ; and A = identity
# can do using constraint2 and constraint6
#we need to define A
#E-step
#Takes 3-mins 
Estep = function(A, l, Y, d, w2 = 0.7, w6 = w2^2){
  #first generate the random orderand loop over them
  random_order = sample(1:length(l),length(l))
  for(i in random_order){
    # now we are going to compute all f ( y h , x i )  and take the min of it
    u = 1
    f2=vector()
    for(j in 1:k){
      f2[j] = distance(A,as.matrix(dtm_train_tfidf[[d]])[i,],Y[j,])
      }
    l[i] = which.min(f2)
  }
  return(l)
}


#Mstep
Mstep = function(A, l, Y, d,w2 = 0.7, w6 = w2^2, eta){
  #update Y first:
  Y=matrix(NA,k,dim(dtm_train_tfidf[[d]])[2])
  for(j in 1:k){
    X = as.matrix(dtm_train_tfidf[[d]])
    Z=as.matrix(X[l==j,],ncol=dim(dtm_train_tfidf[[d]])[2])#subset the Xi to the one with the label
    Y[j,] = col_sums(Z)
    Y[j,] = Y[j,]/(sqrt((t(Y[j,]) %*% A %*% Y[j,])[1]))
  }
  
  
  #update the distance matrix now
  m = dim(A)[1]
  Anew = diag(rep(1,m))
  
  for(u in 1:m){
    add = 0
    for(i in dim(dtm_train_tfidf[[d]])[1]){
      for(j in dim(dtm_train_tfidf[[d]])[1]){
        if(i=j){add=add+0}
        else{ #can use crossprod instead of %*% for faster result
          xi = as.matrix(dtm_train_tfidf[[d]])[i,]
          xj = as.matrix(dtm_train_tfidf[[d]])[j,]
          partial_D_xixj = as.numeric((xi[u] * xj[u] * sqrt((t(xi) %*% A %*% xi)[1]) * sqrt((t(xj) %*% A %*% xj)[1]) - 
  (t(xi) %*% A %*% xj)[1] * (((xi[u])^2 * (t(xj) %*% A %*% xj)[1] + (xj[u])^2 * (t(xi) %*% A %*% xi)[1]) / (2*sqrt((t(xi) %*% A %*% xi)[1]) *sqrt((t(xj) %*% A %*% xj)[1])))) / ((t(xi) %*% A %*% xi)[1] * (t(xj) %*% A %*% xj)[1]))
          
          add = add + partial_D_xixj * (w2 * constraint2(i,j,d) + w6 * constraint6(i,j,d))
        }
      }
    }
    
    for(i in dim(dtm_train[[d]])[1]){
      xi = as.matrix(dtm_train[[d]])[i,]
      y = Y[l[i],]
      partial_D_xiy = (xi[u] * y[u] * sqrt((t(xi) %*% A %*% xi)[1]) * sqrt((t(y) %*% A %*% y)[1]) - 
  (t(xi) %*% A %*% y)[1] * (((xi[u])^2 * (t(y) %*% A %*% y)[1] + (y[u])^2 * (t(xi) %*% A %*% xi)[1]) / (2*sqrt((t(xi) %*% A %*% xi)[1]) *sqrt((t(y) %*% A %*% y)[1])))) / ((t(xi) %*% A %*% xi)[1] * (t(y) %*% A %*% y)[1])
      add = add + partial_D_xiy
    }
    Anew[u,u] = A[u,u] + eta * add
  }
  A=Anew
 
  return(Y)
}
```


EM algorithm completed - to be continued - pseudo-code
```{r}
EM_algorithm = function(A, l, d, t, w2 = 0.7, w6 = w2^t ,epsilon, eta){
  obj = Inf
  A=diag(1,dim(dtm_train_tfidf[[d]])[1],dim(dtm_train_tfidf[[d]])[1])
  k=length(unique(author_id[[d]]))
  while(TRUE){
    #first get the updated l
    l = Estep(A, l, Y, name, d, k , t, w2 = 0.7, w6 = w2**t)
    
    #second, get the updated Y and A
    L = Mstep(A, l, Y, name, d, k , t, w2 = 0.7, w6 = w2**t, eta)
    Y = L[[1]]
    A = L[[2]]
    
    #Get new value of obj and compare to decide wether to stop the algorithm or not
    objnew = objective(A, l, Y, name, d, t, w2 = 0.7, w6 = w2**t)
    
    if(abs(obj-objnew)<epsilon){
      return(l)
    }
    else{
      obj = objnew
    }
  }
}
```


## Step 4: Clustering
```{r}
```

## Step 5: Evaluation

To evaluate the performance of the method, it is required to calculate the degree of agreement between a set of system-output partitions and a set of true partitions. In general, the agreement between two partitioins is measured for a pair of entities within partitions. The basic unit for which pair-wise agreement is assessed is a pair of entities (authors in our case) which belongs to one of the four cells in the following table (Kang et at.(2009)):

\includegraphics[width=500pt]{matching_matrix.png}

Let $M$ be the set of machine-generated clusters, and $G$ the set of gold standard clusters. Then. in the table, for example, $a$ is the number of pairs of entities that are assigned to the same cluster in each of $M$ and $G$. Hence, $a$ and $d$ are interpreted as agreements, and $b$ and $c$ disagreements. When the table is considered as a confusion matrix for a two-class prediction problem, the standard "Precision", "Recall","F1", and "Accuracy" are defined as follows.

$$
\begin{aligned}
\mbox{Precision} &=\frac{a}{a+b}\\
\mbox{Recall}&=\frac{a}{a+c}\\
\mbox{F1} &=\frac{2\times\mbox{Precision}\times\mbox{Recall}}{\mbox{Precision}+\mbox{Recall}}\\
\mbox{Accuracy}&=\frac{a+d}{a+b+c+d}
\end{aligned}
$$

```{r}
source('~/Dropbox/Project4_WhoIsWho/lib/evaluation_measures.R')
matching_matrix_hclust <- matching_matrix(AKumar$AuthorID,result_hclust)
performance_hclust <- performance_statistics(matching_matrix_hclust)
matching_matrix_sclust <- matching_matrix(AKumar$AuthorID,result_sclust)
performance_sclust <- performance_statistics(matching_matrix_sclust)
compare_df <- data.frame(method=c("sClust","hClust"),
                         precision=c(performance_sclust$precision, performance_hclust$precision),
                         recall=c(performance_sclust$recall, performance_hclust$recall),
                         f1=c(performance_sclust$f1, performance_hclust$f1),
                         accuracy=c(performance_sclust$accuracy, performance_hclust$accuracy),
                         time=c(time_sclust,time_hclust))
kable(compare_df,caption="Comparision of performance for two clustering methods",digits = 2)
```

